---
title: "Reproducing Hansen, Lunde and Nason (2011)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reproducing}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

This is the vignette. 

* intro
  + why? illustrate R functions; show correctness; compare to MCS
  + what? application in HLN 2011. which page? which table? 
  
* SW inflation forecasts 

Out-of-sample version
different t-stats
timing?

```{r}
data(SW_infl4cast)
data <- as.matrix(SW_infl4cast)
loss <- (data[, -1] - data[, 1])^2 # compute squared errors

# Estimate MCS same way that Hansen, Lunde, Nason (2011) did.
# Note: "t.min" should not be used in practice.

my_MCS <- estMCS(loss, test = "t.min", B = 25000, l = 12)

my_MCS
```

Results are equivalent (up to rounding and simulation error) in column 1 of page 485 in Hansen, Lunde and Nason (2011).

-->>>>>>>> What is shown in table? Contents??


```{r}
my_MCS[my.MCS[, "MCS p-val"] > 0.1, ] # actual, estimated MCS at alpha = 0.1
```


* Taylor Rule regressions

In-sample version
KLIC, AIC, ...
timing?

* Conclusion
